TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems

### 2017-02-11 ISORC2017/paper.tex
Fix abstract by enago

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems}

@@

Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
TINET is a TCP/IP protocol stack for embedded systems.
Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.
To improve the scalability and configurability, this paper proposes TINET+TECS, a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
TINET+TECS utilizes a dynamic connection method of TECS components to satisfy the original TINET specification.
We evaluate the component-based TINET compared with the original TINET.
Experimental results show that the overheads of execution time and memory consumption are low, and that the configurability is improved.

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems}

@@

% Embedded systems are applied to Internet of Things (IoT), and the high productivity of embedded network software is required.
High productivity embedded network software is required to run embedded systems within the Internet of Things (IoT).
Tomakomai InterNETworking (TINET) is a Transmission Control Protocol/Internet Protocol (TCP/IP) protocol stack for use in embedded systems.
Although TINET is a compact protocol stack, it comprises many complex source codes and is difficult to maintain, extend, and analyze.
To improve scalability and configurability, this paper proposes TINET componentized with the Toyohashi Open Platform for Embedded Real-time Systems (TOPPERS) embedded component system (TINET+TECS), a component-based TCP/IP protocol stack for embedded systems.
This component-based TINET offers software developers high productivity through variable network buffer sizes and the ability to add or remove TCP (or UDP) functionality.
TINET+TECS utilizes a dynamic TECS component connection method to satisfy the original TINET specifications.
The results of an experimental comparison between the proposed component-based and original TINETs show that the execution time and memory consumption overhead are reduced and the configurability is improved.
